TR Invariant T.I.

### 2017-04-10 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] fix a typo.

The eigenvectors are of the form:
\begin{equation}
    \begin{pmatrix}
        \phi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix},\quad \begin{pmatrix}
        \psi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix}
\end{equation}
where
\begin{align}
    \phi &=  (2-m-\cos(p_x)-\cos(p_y))+E_1 \\
    \psi &=  (2-m-\cos(p_x)+\cos(p_y))+E_1
\end{align}
And the have very interesting behavior from $m=-1$ to $m=6$, they
gradually contact and exchange the position of each other
\footnote{You would get more fun if you execute the animation inside
the Mathematica notebook}:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-mN1.pdf}
    \caption{$m=-1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m0.pdf}
    \caption{$m=0$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m1.pdf}
    \caption{$m=1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m2.pdf}
    \caption{$m=2$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m3.pdf}
    \caption{$m=3$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m4.pdf}
    \caption{$m=4$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m6.pdf}
    \caption{$m=6$}
\end{figure}

>>>>

The eigenvectors are of the form:
\begin{equation}
    \begin{pmatrix}
        \phi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix},\quad \begin{pmatrix}
        \psi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix}
\end{equation}
where
\begin{align}
    \phi &=  (2-m-\cos(p_x)-\cos(p_y))+E_1 \\
    \psi &=  (2-m-\cos(p_x)+\cos(p_y))+E_1
\end{align}
And besides crossing each other, they have new interesting behavior as
$m$ varies. When changing from $m=-1$ to $m=6$, they gradually contact
and exchange the position of each other
\footnote{You would get more fun if you execute the animation inside
the Mathematica notebook}:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-mN1.pdf}
    \caption{$m=-1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m0.pdf}
    \caption{$m=0$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m1.pdf}
    \caption{$m=1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m2.pdf}
    \caption{$m=2$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m3.pdf}
    \caption{$m=3$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m4.pdf}
    \caption{$m=4$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m6.pdf}
    \caption{$m=6$}
\end{figure}
